---
title: "Exploring Zika Infection During Pregnancy"
author: "Elizabeth Fogleman"
date: "Date created: `r format(Sys.Date(), '%Y-%m-%d')`"
output: html_document
---

```{r, include = FALSE}
here::i_am("Rmd/Zika_Report.Rmd")
knitr::opts_knit$set(root.dir = here::here())
```

$~$ <!--This adds space between header and next section--> 

The goal of this (fictional, simulated) study was to understand the association between Zika virus exposure during pregnancy and various infant outcomes.

## Maternal data
Data was captured on 3,500 pregnant women. Maternal demographics at study entry are summarized in table 1 below. A majority of women were between 20-35 years old and highest level of education obtained across all sites was predominantly primary or secondary school. Moreover, 81.5% of women were enrolled during their 1st trimester of pregnancy. Most participants had two or less prior pregnancies.


__Table 1__. Maternal Demographics at Study Entry

```{r, echo = FALSE}
load(here::here("Output", "maternal_table.rdata"))

mat_table
```


$~$ <!--This adds space between header and next section--> 

## Infant Data
Various infant outcomes were assessed by Zika exposure status, including stillbirth or neonatal death, preterm birth, microcephaly, low birth weight, seizure, arthrogryposis, congenital malformations, and audiological and ophthalmological failures.

__Table 2__. Infant Characteristics at Birth

```{r, echo = FALSE}
load(here::here("Output", "infant_table.rdata"))

inf_table
```

$~$ <!--This adds space between header and next section--> 



